Wilcoxon results tables - text and appendix

### 2018-02-06 analyses/06-table-wilcox.Rmd
Edits to reshape the data - spread no longer working due to duplicate rows so I've gone back to reshape. This required some renames to match the rest of the code.

# Extract proximity and gradual split models
# Remove excess columns
# Add model column name
fix.wilcox <- function(data){
  data %>%
  select(-c(V1,V2)) %>%
  filter(V3 == "proximity" | V3 == "gradual.split") %>%
  spread(V4, V6) %>%
  arrange(V5) %>%
  rename(model = V3) %>%
  rename(period = V5)  
}

@@

```{r}
# Remove excess columns
# Add model column name
fix.wilcox.appendix <- function(data){
  data %>%
  select(-c(V1,V2)) %>%
  spread(V4, V6) %>%
  arrange(V5) %>%
  rename(model = V3) %>%
  rename(period = V5)
}

>>>>

# Extract proximity and gradual split models
# Remove excess columns
# Add model column name
fix.wilcox <- function(data){
  data %>%
  select(-c(V1,V2)) %>%
  filter(V3 == "proximity" | V3 == "gradual.split") %>%
  reshape(idvar = c("V3","V5"), timevar = "V4", direction = "wide") %>%
  arrange(V5) %>%
  rename(model = V3) %>%
  rename(period = V5) %>%
  rename(stratigraphy = V6.stratigraphy) %>%
  rename(duration = V6.duration) %>%
  rename(number = V6.number) 
}

@@

```{r}
# Remove excess columns
# Add model column name
fix.wilcox.appendix <- function(data){
  data %>%
  select(-c(V1,V2)) %>%
  reshape(idvar = c("V3","V5"), timevar = "V4", direction = "wide") %>%
  arrange(V5) %>%
  rename(model = V3) %>%
  rename(period = V5) %>%
  rename(stratigraphy = V6.stratigraphy) %>%
  rename(duration = V6.duration) %>%
  rename(number = V6.number) 
}
